---
title: "KableExtra Table"
author: "Eric Anjeo"
date: "10/11/2020"
always_allow_html: true
output: github_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message = F)
```

## KableExtra Table

I will walk you through the different type of tables that can be generated by KableExtra package at the very basic level. There are many other packages that can be used in building and formatting tables, but for this particular course we will restrict ourselves to the aforementioned package. The gapminder data will be used in the creation of the different tables. This tables cannot be created for word template it is only for HTML.

```{r}
#install.packages("kableExtra") run this command if you have not installed the package by removing the hash.
library(kableExtra)#call the command that contains functions to be used.
library(gapminder)#contains the data to be used. If you do not have please install.
```

## __Introduction__

The data will consist of six observations that will remain constant to the different tables styling that it will be subjected on. The basic command in base R is the head() command that will automatically return six observations whenever called.

```{r}
library(tidyverse)# for data wrangling
df <- gapminder %>% sample_n(6)
#The base r command will return
gapminder %>% sample_n(6)%>% head()
```

## Simple KableExtra tables

```{r}
df %>% kable()# kable() and kbl() produce same output when called
df %>% kbl()
```

## Adding themes

Themes makes tables look appealing. There are different options that one can apply so as to make the tables awesome.

```{r}
df %>% kable() %>% kable_styling()
```

The above table is slightly better than the one we created before this. kable-styling() has improved it. Now it is time to add the different parameters.

## Still moving on 

```{r}
df %>% kable() %>% kable_styling('hover',full_width = T)
```

By including th hover option, we can now be able to mover the table through each observation. This feature is just amazing.

## Other themes that can be used

kable styling is one of the themes that can be used for customization. We look into other themes.

Theme: kable_paper

```{r}
df %>% kable() %>% kable_paper('hover',full_width=T)
```

### 

    Theme:kable_classic

```{r}
df %>% kbl(caption = 'sample gapminder') %>% kable_classic('hover')
```

### 

Theme: kable classic2

```{r}
df %>% kbl(caption = 'sample gapminder') %>% kable_classic_2('hover')
```

### 

Theme: Kable_minimal()

```{r}
df %>% kbl(caption = 'sample gapminder') %>% kable_minimal('hover')
```

### 

Theme:

    kable_material()

```{r}
df %>% kbl(caption = 'sample gapminder') %>% kable_material('hover')
```

    kable_material_dark()

```{r}
df %>% kbl(caption = 'sample gapminder') %>% kable_material_dark('hover')
```

## Table Styling Features.

We look at the different features of kable -styling(). The stripped feature, will create different colors between observations that will be repeated for all other observation. The Full width feature will zoom you table to the entire screen, it default is true but it can be changed. The option position places the table in the center, right or left.

```{r}
df %>% kbl(caption = 'sample gapminder') %>%kable_styling(bootstrap_options = c('hover','striped'))
```

Time to put the full feature to false.

```{r}
df %>% kbl(caption = 'sample gapminder') %>%kable_styling(bootstrap_options = 'striped',full_width=F)
```

When try to adjust the position of the table

Left

```{r}
df %>% kbl(caption = 'sample gapminder') %>%kable_styling(bootstrap_options ='striped',position = 'float_left',full_width=F)
```